---
title: "XgfRiction Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{XgfRictionVignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(XgfRiction)
```

Let's first start by loading in the data frame that we will be working with. In this case, we are loading in data from a local file on a computer.

```{r}

file_path <- "~/Documents/GitHub/XgfRictionn/XgfRiction/ExampleData.csv"

# Load the data from the CSV file
ExampleData <- read.csv(file_path)

# Check the structure of the loaded data
str(ExampleData)
```

# XGFrictionProcessor Class 

The XGFrictionProcessor class represents a processor specifically designed for handling eddy covariance data. This class is equipped with methods to initialize the processing of eddy covariance data.

Fields site: The name of the site associated with the processor. Methods initialize(site):

Description: Constructor method for the XGFrictionProcessor class. Parameters: site: Character string representing the name of the site. Usage: processor \<- XGFrictionProcessor\$new(site) initialize_xgfriction_processing(dataframe, LatDeg, LongDeg, TimeZoneHour):

Description: Method to initialize the processing of eddy covariance data. Parameters: dataframe: The data frame containing XGFriction data. LatDeg: Latitude of the site in degrees. LongDeg: Longitude of the site in degrees. TimeZoneHour: Time zone offset in hours. Usage:

```{r}
processor <- XGFrictionProcessor$new(site = "Bart")
# Initialize XGFriction processing with ExampleData

# Initialize XGFriction processing with ExampleData
processor <- processor$initialize_xgfriction_processing(dataframe = ExampleData, LatDeg = 45.0, LongDeg = -75.0, TimeZoneHour = -5)

# Check the structure of the processor object
print(processor)

```
