---
title: "XgfRiction Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{XgfRictionVignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

#Load the necessary libraries

```{r setup}
library(XgfRiction)


#dependancies 
library(XgfRiction)


#other libraries 
library(roxygen2)
library(devtools)
library(REddyProc)
library(Metrics)
library(stats)
library(tidymodels)
library(ggplot2)
library(parsnip)
library(tune)
library(base)
library(rsample)
library(caret)
library(xgboost)
library(pkgdown)
```

Let's first start by loading in the data frame that we will be working with. In this case, we are loading in data from a local file on a computer.

```{r}

file_path <- "~/Documents/GitHub/XgfRictionn/XgfRiction/ExampleData.csv"

# Load the data from the CSV file
ExampleData <- read.csv(file_path)

# Check the structure of the loaded data
str(ExampleData)

```

# XgfRiction_initialize Function Description

The XgfRiction_initialize function is a utility provided by the XgfRiction package to initialize an XGFrictionProcessor object for processing eddy covariance data. This function simplifies the setup process by automating the initialization of the processor object with essential parameters such as site ID, column names, POSIX time column, and location information.

Arguments: site_ID: Site ID from the AmeriFlux website. data: Data frame containing the eddy covariance data. column_names: Vector with selected column names from the data frame. posix_time_column: Column name containing POSIX time stamps. LatDeg: Latitude of the measurement site. LongDeg: Longitude of the measurement site. TimeZoneHour: Time zone offset in hours. Returns: An initialized XGFrictionProcessor object ready for further data processing and analysis.

```{r}
# Set your site ID
site_ID <- "US-Bar"

# Set your column names
column_names <- c("NEE", "Rg", "Tair", "VPD", "Ustar")

# Set your POSIX time column
posix_time_column <- "TIMESTAMP"

# Set your site location information
LatDeg <- 44.0646
LongDeg <- -71.2881
TimeZoneHour <- -5

# Initialize sEddyProc object
processor <- XgfRiction_initialize(site_ID = site_ID,
                                   data = ExampleData,
                                   column_names = column_names,
                                   posix_time_column = 'TIMESTAMP',
                                   LatDeg = LatDeg,
                                   LongDeg = LongDeg,
                                   TimeZoneHour = TimeZoneHour)


```

# \#### Initialize XGFriction Processor

The `initialize_xgfriction_processor` function is responsible for initializing the XGFriction processor object within the XGFriction package. This processor object serves as an interface for various operations related to XGFriction data, providing a structured environment for data handling and analysis. By creating an instance of this processor object, users can access and utilize the functionalities offered by the XgfRiction package in a convenient and organized manner.

```{r}
processor <- XGFrictionProcessor$new(site = "Bart")
# Initialize XGFriction processing with ExampleData

# Initialize XGFriction processing with ExampleData
processor <- processor$initialize_xgfriction_processing(dataframe = ExampleData, LatDeg = 45.0, LongDeg = -75.0, TimeZoneHour = -5)

# Check the structure of the processor object
print(processor)

```
